### 2018-06-27 Thesis/Parts/Data/Data.tex
discussion & presentation
minor changes
Spelling check

\header{Datasets}
For this researched we used a (pre-made) tokenized dataset, which reduces the total amount of words by 34\%, from this tokenized set, we created the embeddings and the TF-IDF feature vectors.
\subheader{Tokenization}
The following steps have been applied to the words to create a tokenized set:
\begin{enumerate}
\item{Removed punctuation}
\item{Removed all non-ascii characters}
\item{Transformed all characters to lower-case}
\item{Removed stop-words, as provided by the NLTK library}
\item{Removed numbers}
\item{Stemmed all words, using the stemmer provided by the NLTK library}
\end{enumerate}
These transformations reduced our dataset by 34\%, resulting in a tokenized set of $186.962.354$ tokens.

\subheader{Embedding}
For this research we reused the word embeddings created by \citet{Truong2017Thesis}. These embeddings have a vector size of 300, which is an industry default. They have been trained on the entire Elsevier corpus, not limited to the subset we used for this research. To construct article embeddings we take the average of all normalized word embeddings for that article. Journal embeddings are constructed in the same way, we averaged all the normalized article embeddings to create the journal embeddings. We have used multiple embedding configurations for this research
\subsubheader{Default embedding}
The default embedding is created form the pre-trained word embeddings, no modifications have been applied to this set.
\subsubheader{TF-IDF embedding}
The TF-IDF weighted embedding set, referred to as TF-IDF embedding, are the default word embeddings weighted with a TF-IDF score per word.\\
The TF-IDF is calculated with a raw token count, and a smoothed inverted document frequency, calculated as follows:\\
\begin{equation}
IDF = \log_{10}(\dfrac{|A|}{|A_t|})
\end{equation}
Where $|A|$ is the total count of articles and $|A_t|$ is the count of articles containing term t.
The articles embeddings are a normalized summation of each word vector multiplied by it TF-IDF value. Since we take a sum of all words, the Term Frequency is embedded as the raw count of each word.
\subsubheader{10K TF-IDF embedding}
The 10K embedding set is generated similarity to the TF-IDF embedding, this version only uses the 10.000 most common tokens, reducing the amount of tokens it uses. This set was created to see if the limitation to 10.000 tokens reduces the amount of noise, and with that increasing the performance.
\subsubheader{5K TF-IDF embedding}
The 5K TF-IDF embedding is the TF-IDF embedding set, limited to the 5.000 most common words. This set was created to more aggressively limit the amount of tokens, and with that, cancel out more noise.
\subsubheader{1K-6K TF-IDF embedding}
The 1K-6K TF-IDF embedding is the TF-IDF embedding limited to the top 6.000 most common words, without the top 1.000 most common words. The rationale for this is that common words will occur in many articles, creating noise, by cutting of the top 1.000 and cutting of everything below 6.000 we tried to reduce the noise by filtering common words. This cut results in a set of 5.000 tokens, which allows us to compare it to the 5K TF-IDF set.

\subheader{TF-IDF}
To create the TF-IDF feature vectors, we used the TF-IDF model and a hasher from pysparks the MlLib library. The TF-IDF feature vectors are created by hashing the tokens with the hasher, which has a set hash bucket size. These hashed values are passed on to the TF-IDF model, resulting in a feature vector which vector dimensions equals the amount of hash buckets. To limit the computational and storage expenses and to reduce noise by rare words, we limit our vocabulary size.
We denote the TF-IDF configurations as follows: $vocabulary size/hashbucket size$. Furthermore, we denote 1.000 as 1K, since we deal with chosen values which can be exactly noted given this notation.
\begin{figure}
\includegraphics[width=6in]{Plots/tfidf_selection_plot}
\caption{TF-IDF performance and memory usage}\label{figure:tfidfPerformance}
\end{figure}
\FloatBarrier
Figure~\ref{figure:tfidfPerformance} shows the performance, as median rank, and storage size, in gigabyte, of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations. This plot shows that, while the required storage size keeps rising, the performance on title quickly stagnates, and the performance on abstract follows too. Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to. The TF-IDF features are created on article level. We average the set of article embeddings to create a journal embedding.

@@

\subheader{Create training and validation set}
We split our initial set  $80\%$ - $20\%$,. We use the $80\%$ set as the training set for the journal representations, and the $20\%$ set as the validation set for the journal representations. This split is based on a random number given to article each record, ensuring that all set have the same (random) training and validation set.
\subheader{Create journal embeddings}
From our training set we create the journal embeddings, which are created for most sets\footnote{see paragraph datasets} by averaging the article embeddings or feature vectors.
\subheader{Categorize validation articles}
To categorize the articles, we calculate the distance between the title- and abstract embedding of each article, from the validation set, to the title- and abstract embedding of each journal, during this process we keep track of:
\begin{itemize}
\item{Title-based-rank of the actual journal}
\item{Abstract-based-rank of the actual journal}
\item{Best scored journal on the abstract similarity}
\item{Best scored journal on the title similarity}
\item{Abstract similarity between the actual journal and the article}
\item{Title similarity between the actual journal and the article}
\end{itemize}
\subsubheader{Distance metrics}
To calculate the distance between to vectors, cosine similarity is commonly used. We validated the quality of cosine similarity as a distance metrics by comparing it to all other similarity matrices available in the SciPy library, which we used to calculate the distances. We calculate the similarities based on the normalized embeddings, and compared the distance metrics based on the default embedding set. Table~\ref{table:distanceMetrics} shows the results of this validation.\\
\begin{table}[hbt]
\begin{tabular}{|l|l|l|l|l|}
\hline
Metric\footnote{As defined and provided by the SciPy library} & Median title rank & Average title rank & Median abstract rank & Average abstract rank  \\
\hline
Braycurtis & 28 & 130 & 23 & 124  \\
\hline
Canberra & 33 & 148 & 26 & 133  \\
\hline
Chebyshev & 57 & 256 & 41 & 191  \\
\hline
\textit{Cityblock} & \textit{28} & \textit{130} & \textit{23} & \textit{124}  \\
\hline
\textit{Correlation} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
\hline
\textbf{Cosine} & \textbf{27} & \textbf{127} & \textbf{23} & \textbf{122}  \\
\hline
Dice & 1995 & 1929 & 1995 & 1929  \\
\hline
\textit{Euclidean} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
\hline
Hamming & 1995 & 1929 & 1995 & 1929  \\
\hline
Jaccard & 1995 & 1929 & 1995 & 1929  \\
\hline
Kulsinski & 1995 & 1929 & 1995 & 1929  \\
\hline
Mahalanobis & 136 & 544 & 75 & 449  \\
\hline
Matching & 1995 & 1929 & 1995 & 1929  \\
\hline
Rogerstanimoto & 1995 & 1929 & 1995 & 1929  \\
\hline
Russellrao & 1995 & 1929 & 1995 & 1929  \\
\hline
\textit{Seuclidean} & \textit{27} & \textit{124} & \textit{22} & \textit{115}  \\
\hline
Sokalmichener & 1995 & 1929 & 1995 & 1929  \\
\hline
Sokalsneath & 1995 & 1929 & 1995 & 1929  \\
\hline
\textit{Sqeuclidean} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
\hline
Yule & 1995 & 1929 & 1995 & 1929  \\
\hline
\end{tabular}
\caption{Distance metric performance for word embeddings on the categorization of academic texts}\label{table:distanceMetrics}
\end{table}
These results show high similarity between cosine-based metrics (Cosine \& Correlation) and euclidean based metrics (Euclidean, Seuclidean \& Sqeuclidean). This similarity is expected, since the cosine and euclidean distances should yield the same results on normalized sets. The results show that some enhancement on the euclidean algorithm result in slightly improved results, although not significant. Also the Cityblock metric yields results close to the Cosine metric, it has a slightly worse performance, which is also not significant. Because of this, we will use the cosine-similarity as the distance matrix, which will make our results better comparable with other work.

\subheader{Performance measurement}
We use multiple metrics to validate the performance of the embedding sets and TF-IDF sets on the categorization task. These metrics are:
\begin{enumerate}
\item{F1-score}
\item{Median \& average rank}
\item{Rank distribution}
\end{enumerate}
\subsubheader{F1-score}
We define the positive \& negative metrics as follows:\\
\begin{jumpin}
$True Positive = $ Articles that are correctly matched to the current journal\\
$False Positive = $ Articles that are incorrectly matched to other journals\\
$False Negative = $ Articles that are incorrectly matched to the current journal\\
\end{jumpin}
We used these metrics to calculate the Recall, Precision \& F1 as follows:\\
\begin{jumpin}
$Recall = \dfrac{True Positive}{True Positive + False Negative}$\vspace{0.1in}\\
$Precision = \dfrac{True Positive}{True Positive + False Positive}$\vspace{0.1in}\\
$F1 = \dfrac{2 * Precision * Recall}{Precision + Recall}$
\end{jumpin}
\subsubheader{Median \& average rank}
We use the median rank to indicate around which rank the 'standard' article would be ranked, based on its title or abstract. We do this by taking the median of the respective rank from each article. This gives us an indication of the behaviour of most articles in our validation set. This median rank (mostly) ignores the outliers, we therefore also use the average rank, which gives a more global indication, although this rank may be over-influenced by some outliers.
\subsubheader{Rank distribution}
To further analyse the ranking results, we plot the rank distribution to get an indication of the ranking-landscape.

\header{Two dimensional plot}
To create a plot, we transformed the 300-dimensional journal vectors into 2-dimensional vectors using TSNE based on pca\footnote{Principal component analysis}. These 2-dimensional vectors, representing the x \& y coordinate, can then be drawn in a plot. To visualize the preservation of journal-relatedness while converting the 300 dimensions to 2 dimension, we create groupings using k-means. These groupings are created on the 300-dimensional vectors, and are visualized in the plot using colors.
\end{document}

% RAW DATA:
% 1,391,543 articles
% 14 811 433 title tokens			230805 unique		18.822.399			939.665
% 172 150 921 abstract tokens		738961 unique		264.653.020			5.853.077
% 186 962 354 total tokens			763475 unique		283.475.419			6.209.769
% 3,759 journals

% split = 79.9509609117 - 20.0490390883

% training numbers
% 10K = percentage?}

>>>>

\header{Datasets}
For this researched we used a (pre-made) tokenized dataset, which reduces the total amount of words by 34\%, from this tokenized set, we created the embeddings and the TF-IDF feature vectors.
\subheader{Tokenization}
The following steps have been applied to the words to create a tokenized set:
\begin{enumerate}
\item{Removed punctuation}
\item{Removed all non-ASCII characters}
\item{Transformed all characters to lower-case}
\item{Removed stop-words, as provided by the NLTK library}
\item{Removed numbers}
\item{Stemmed all words, using the stemmer provided by the NLTK library}
\end{enumerate}
These transformations reduced our dataset by 34\%, resulting in a tokenized set of $186.962.354$ tokens.

\subheader{Embedding}
For this research, we reused the word embeddings created by \citet{Truong2017Thesis}. These embeddings have a vector size of 300, which is an industry default. They have been trained on the entire Elsevier corpus, not limited to the subset we used for this research. To create article embeddings, we take the average of all normalized word embeddings for that article. Journal embeddings are created in the same way. We averaged all the normalized article embeddings to create the journal embeddings. We have used multiple embedding configurations for this research
\subsubheader{Default embedding}
The default embedding is created form the pre-trained word embeddings; no modifications have been applied to this set.
\subsubheader{TF-IDF embedding}
The TF-IDF weighted embedding set, referred to as TF-IDF embedding, are the default word embeddings weighted with a TF-IDF score per word.\\
The TF-IDF is calculated with a raw token count, and a smoothed inverted document frequency, calculated as follows:\\
\begin{equation}
IDF = \log_{10}(\dfrac{|A|}{|A_t|})
\end{equation}
Where $|A|$ is the total count of articles and $|A_t|$ is the count of articles containing term t.
The articles embeddings are a normalized summation of each word vector multiplied by it TF-IDF value. Since we take a sum of all words, the Term Frequency is embedded as the raw count of each word.
\subsubheader{10K TF-IDF embedding}
The 10K embedding set is generated similarity to the TF-IDF embedding, this version only uses the 10.000 most common tokens, reducing the number of tokens it uses. This set was created to see if the limitation to 10.000 tokens reduces the amount of noise, increasing the performance.
\subsubheader{5K TF-IDF embedding}
The 5K TF-IDF embedding is the TF-IDF embedding set, limited to the 5.000 most common words. This set was created to limit the number of tokens more aggressively, and with that, cancel out more noise.
\subsubheader{1K-6K TF-IDF embedding}
The 1K-6K TF-IDF embedding is the TF-IDF embedding limited to the top 6.000 most common words, without the top 1.000 most common words. The rationale for this is that common words will occur in many articles, creating noise, by cutting off the top 1.000 and cutting off everything below 6.000 we tried to reduce the noise by filtering common words. This cut results in a set of 5.000 tokens, which allows us to compare it to the 5K TF-IDF set.

\subheader{TF-IDF}
To create the TF-IDF feature vectors, we used the TF-IDF model and a hasher from PySparks MlLib library. The TF-IDF feature vectors are created by hashing the tokens with the hasher, which has a set hash bucket size. These hashed values are passed on to the TF-IDF model, resulting in a feature vector which vector dimensions equal the number of hash buckets. To limit the computational and storage expenses and to reduce noise by rare words, we limit our vocabulary size.
We denote the TF-IDF configurations as follows: $vocabulary size/hash bucket number$. Furthermore, we denote 1.000 as 1K, since we deal with chosen values which can be exactly noted given this notation.
\begin{figure}
\includegraphics[width=6in]{Plots/tfidf_selection_plot}
\caption{TF-IDF performance and memory usage}\label{figure:tfidfPerformance}
\end{figure}
\FloatBarrier
Figure~\ref{figure:tfidfPerformance} shows the performance, as median rank, and storage size, in gigabyte, of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations. This plot shows that, while the required storage size keeps rising, the performance on title quickly stagnates, and the performance on abstract follows too. Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to. The TF-IDF features are created on article level. We average the set of article embeddings to create a journal embedding.

@@

\subheader{Create training and validation set}
We split our initial set  $80\%$ - $20\%$. We use the $80\%$ set as the training set for the journal representations, and the $20\%$ set as the validation set for the journal representations. This split is based on a random number given to article each record, ensuring that all set have the same (random) training and validation set.
\subheader{Create journal embeddings}
From our training set we create the journal embeddings, which are created for most sets\footnote{see paragraph datasets} by averaging the article embeddings or feature vectors.
\subheader{Categorize validation articles}
To categorize the articles, we calculate the distance between the title- and abstract embedding of each article, from the validation set, to the title- and abstract embedding of each journal, during this process we keep track of:
\begin{itemize}
\item{Title-based-rank of the actual journal}
\item{Abstract-based-rank of the actual journal}
\item{Best scored journal on the abstract similarity}
\item{Best scored journal on the title similarity}
\item{Abstract similarity between the actual journal and the article}
\item{Title similarity between the actual journal and the article}
\end{itemize}
\subsubheader{Distance metrics}
To calculate the distance between to vectors, cosine similarity is commonly used. We validated the quality of cosine similarity as a distance metrics by comparing it to all other similarity matrices available in the SciPy library, which we used to calculate the distances. We calculate the similarities based on the normalized embeddings, and compared the distance metrics based on the default embedding set. Table~\ref{table:distanceMetrics} shows the results of this validation.\\
\begin{table}[hbt]
\begin{tabular}{|l|l|l|l|l|}
\hline
Metric\footnote{As defined and provided by the SciPy library} & Median title rank & Average title rank & Median abstract rank & Average abstract rank  \\
\hline
Braycurtis & 28 & 130 & 23 & 124  \\
\hline
Canberra & 33 & 148 & 26 & 133  \\
\hline
Chebyshev & 57 & 256 & 41 & 191  \\
\hline
\textit{Cityblock} & \textit{28} & \textit{130} & \textit{23} & \textit{124}  \\
\hline
\textit{Correlation} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
\hline
\textbf{Cosine} & \textbf{27} & \textbf{127} & \textbf{23} & \textbf{122}  \\
\hline
Dice & 1995 & 1929 & 1995 & 1929  \\
\hline
\textit{Euclidean} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
\hline
Hamming & 1995 & 1929 & 1995 & 1929  \\
\hline
Jaccard & 1995 & 1929 & 1995 & 1929  \\
\hline
Kulsinski & 1995 & 1929 & 1995 & 1929  \\
\hline
Mahalanobis & 136 & 544 & 75 & 449  \\
\hline
Matching & 1995 & 1929 & 1995 & 1929  \\
\hline
Rogerstanimoto & 1995 & 1929 & 1995 & 1929  \\
\hline
Russellrao & 1995 & 1929 & 1995 & 1929  \\
\hline
\textit{Seuclidean} & \textit{27} & \textit{124} & \textit{22} & \textit{115}  \\
\hline
Sokalmichener & 1995 & 1929 & 1995 & 1929  \\
\hline
Sokalsneath & 1995 & 1929 & 1995 & 1929  \\
\hline
\textit{Sqeuclidean} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
\hline
Yule & 1995 & 1929 & 1995 & 1929  \\
\hline
\end{tabular}
\caption{Distance metric performance for word embeddings on the categorization of academic texts}\label{table:distanceMetrics}
\end{table}
These results show high similarity between cosine-based metrics (Cosine \& Correlation) and euclidean based metrics (Euclidean, Seuclidean \& Sqeuclidean). This similarity is expected, since the cosine and euclidean distances should yield the same results on normalized sets. The results show that some enhancement on the euclidean algorithm result in slightly improved results, although not significant. Also the Cityblock metric yields results close to the Cosine metric, it has a slightly worse performance, which is also not significant. Because of this, we will use the cosine-similarity as the distance matrix, which will make our results better comparable with other work.

\subheader{Performance measurement}
We use multiple metrics to validate the performance of the embedding sets and TF-IDF sets on the categorization task. These metrics are:
\begin{enumerate}
\item{F1-score}
\item{Median \& average rank}
\item{Rank distribution}
\end{enumerate}
\subsubheader{F1-score}
We define the positive \& negative metrics as follows:\\
\begin{jumpin}
$True Positive = $ Articles that are correctly matched to the current journal\\
$False Positive = $ Articles that are incorrectly matched to other journals\\
$False Negative = $ Articles that are incorrectly matched to the current journal\\
\end{jumpin}
We used these metrics to calculate the Recall, Precision \& F1 as follows:\\
\begin{jumpin}
$Recall = \dfrac{True Positive}{True Positive + False Negative}$\vspace{0.1in}\\
$Precision = \dfrac{True Positive}{True Positive + False Positive}$\vspace{0.1in}\\
$F1 = \dfrac{2 * Precision * Recall}{Precision + Recall}$
\end{jumpin}
\subsubheader{Median \& average rank}
We use the median rank to indicate at which rank the 'standard' article would be ranked, based on its title or abstract. We do this by taking the median of the respective rank from each article. This gives us an indication of the behaviour of the articles in our validation set. This median rank (mostly) ignores the outliers, we therefore also use the average rank, which gives a more global indication, although this rank may be over-influenced by some outliers.
\subsubheader{Rank distribution}
To further analyse the ranking results, we plot the rank distribution to get an indication of the ranking-landscape.

\header{ Two-dimensional plot}
To create a plot, we transformed the 300-dimensional journal vectors into 2-dimensional vectors using TSNE based on pca\footnote{Principal component analysis}. These 2-dimensional vectors, representing the x \& y coordinate, can then be drawn in a plot. To visualize the preservation of journal-relatedness while converting the 300 dimensions to 2 dimensions, we create groupings using k-means. These groupings are created on the 300-dimensional vectors and are visualized in the plot using colors. We use the k-means groupings due to the lack of subject-based grouping values in our dataset.
\end{document}

### 2018-06-27 Thesis/Parts/Future_work/Future_work.tex
Spelling check

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Future work}
This research focussed on the quality of word embeddings on academic texts. To do this we used both a comparison to TF-IDF and a visualization of the word embeddings. Future works may seek to further improve the quality of the word embeddings.

\subheader{Method differences}
\citet{levy2015improving} observed that there were no major differences between the various embedding creation methods. They state that the difference in performance is mainly caused by the global/hyper parameters. In this research, we have not looked at comparison between various models and/or (hyper) parameters. We instead used a standard configuration, to focus more on the actual performance of the embeddings, instead of the best-possible performance. Future work could seek to validate the results of \citet{levy2015improving} by expanding our research with multiple metrics. It should be noted however that Levy et al. base their conclusions on word similarity and word analogy tasks, and not on categorization. This is the reason why we did not take this research into account in our discussion, since their experiments are not comparable to ours.

\subheader{Intelligent cutting}
An interesting improvement to enhance the word embeddings with could be a smarter way to remove noise, based on word embeddings. This might be achieved by analysing the word embedding spectrum before normalization, and to then cut the center of the vector space out. This must be applied before normalization, since normalization causes all embeddings to have a distance of 1 to the center point. All words which are generic are in the center of the spectrum. Removing these words prevents the larger texts to be pulled towards the middle, where they lose the parts of their meaning which sets them apart from the other journals. We expect that this way of cutting, instead of word-occurrence cutting, will improve the quality of the word embeddings.

\subheader{Text combination}
To cope with the problem of articles that do have an abstract but no title, or vice versa, it would be interesting to see what the quality of the embeddings would be if both texts were combined into one text. This should be possible since title and abstract per article share a common topic. We would expect that the common text would have the quality of the abstract, which is according to our findings the part that is best usable for the embeddings and TF-IDF.

@@

\subheader{Reversed word pairs}
At this point in time, there are no domain specific word pair sets available. However, as we demonstrated, we can still test the quality of word embeddings. Once we established that we have word vectors of high quality, could we create word pairs from the embeddings? If this is the case, we could reverse-engineer domain specific word pair sets for future use. These word pairs should most likely still be validated by humans, but the automatic generation of word pairs should already reduce the effort needed for this process.

\subheader{Historical overview}
We have shown that the word embeddings can be used to create a subject spectrum, in which we plotted all the articles of one year. This gives insight into the currently popular research field, indicated by dense areas on the plot. If we would create this plot over multiple years, and then show these years in chronological order, we should be able to see the evaluation of research fields in time, giving more insight in shifting interests and the development of new research areas.

\subheader{TF-IDF top-cutoff}
In our research we used a dataset from which we removed the top 1k words, together with everything beyond 6k. This dataset did not perform well in our research, future work could look into this by validating if the top-words cut-off decreases the TF-IDF performance. Our findings on this topic are minimal, although we can say that we would not expect that the top-cutoff improves the performance, since a set with the top 5k words performed better than the 1k till 6k words set.

\subheader{Collecting a set of terms}
Our results show that, for larger texts, TF-IDF outperforms the embeddings. Given this, it would be logical to use TF-IDF for search tasks on sets with many tokens. However, the search term itself will contain a small amount of tokens, as our research showed, embeddings perform better in this situation. Future work could try to combine these findings, by collecting a large amount of words, resembling the meaning (captured by the embeddings), and transforming this into a large collection of words (mimicking word occurrence, captured by the TF-IDF). If this could be done effectively, the power of the TF-IDF method could be applied to smaller texts. This process could be seen as a translation from word-embedding space into TF-IDF space. Further more, it would be interesting to see which words would be selected, and if these words represent the given sentence as an "extracted version" which would still be interpretable by humans.
\end{document}

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Future work}
This research focussed on the quality of word embeddings on academic texts. To do this, we used both a comparison to TF-IDF and a visualization of the word embeddings. Future works may seek to improve the quality of the embeddings further or determine the limit of the capabilities of the embedding technique.

\subheader{Method differences}
\citet{levy2015improving} observed that there were no significant differences between the various embedding creation methods. They state that the global/hyperparameters mainly cause the difference in performance. In this research, we have not looked at the comparison between various models and (hyper) parameters. We instead used a standard configuration, to focus more on the actual performance of the embeddings, instead of the best possible performance. Future work could seek to validate the results of \citet{levy2015improving} by expanding our research with multiple metrics. It should be noted however that Levy et al. base their conclusions on word similarity and word analogy tasks, and not on categorization. This is the reason why we did not take this research into account in our discussion since their experiments are not comparable to ours.

\subheader{Intelligent cutting}
An interesting improvement to enhance the word embeddings with could be a smarter way to remove noise, based on word embeddings. This might be achieved by analyzing the word embedding spectrum before normalization, and to then cut the center of the vector space out. This must be applied before normalization since normalization causes all embeddings to have a distance of 1 to the center point. All words which are generic are in the center of the spectrum. Removing these words prevents the larger texts to be pulled towards the middle, where they lose the parts of their meaning which sets them apart from the other journals. We expect that this way of cutting, instead of word-occurrence cutting, will improve the quality of the word embeddings.

\subheader{Text combination}
To cope with the problem of articles that do have an abstract but no title, or vice versa, it would be interesting to see what the quality of the embeddings would be if both texts were combined into one text. This should be possible since title and abstract per article share a common topic. We would expect that the common text would have the quality of the abstract, which is according to our findings the part that is best used for the embeddings and TF-IDF.

@@

\subheader{Reversed word pairs}
At this point, there are no domain-specific word pair sets available. However, as we demonstrated, we can still test the quality of word embeddings. Once we established that we have word vectors of high quality, could we create word pairs from the embeddings? If this is the case, we could reverse-engineer domain specific word pair sets for future use. These word pairs should most likely still be validated by humans, but the automatic generation of word pairs should already reduce the effort needed for this process.

\subheader{Historical overview}
We have shown that the word embeddings can be used to create a subject spectrum, in which we plotted all the articles for one year. This gives insight into the currently popular research field, indicated by dense areas on the plot. If we would create this plot over multiple years, and then show these years in chronological order, we should be able to see the evaluation of research fields in time, giving more insight in shifting interests and the development of new research areas.

\subheader{TF-IDF top-cutoff}
In our research, we used a dataset from which we removed the top 1k words, together with everything beyond 6k. This dataset did not perform well in our research; future work could look into this by validating if the top-words cut-off decreases the TF-IDF performance. Our findings on this topic are minimal, although we can say that we would not expect that the top-cutoff improves the performance since a set with the top 5k words performed better than the 1k till 6k words set.

\subheader{Collecting a set of terms}
Our results show that, for larger texts, TF-IDF outperforms the embeddings. Given this, it would be logical to use TF-IDF for search tasks on sets with many tokens. However, the search term itself will contain a small number of tokens, as our research showed, embeddings perform better in this situation. Future work could try to combine these findings, by collecting a large number of words, resembling the meaning (captured by the embeddings), and transforming this into a (large) collection of words (mimicking word occurrence, captured by the TF-IDF). If this could be done effectively, the power of the TF-IDF method could be applied to smaller texts. This process could be seen as a translation from word-embedding space into TF-IDF space. Furthermore, it would be interesting to see which words would be selected and if these words represent the given sentence as an "extracted version" which would still be interpretable by humans.
\end{document}

### 2018-06-27 Thesis/Parts/Motivation/Motivation.tex
Spelling check

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Motivation}
\subheader{In-domain embeddings and validation}
In earlier research concerning domain specific articles,  \citet{Truong2017Thesis} found that in-domain training of the word embeddings can  improve the process of document clustering. The usage of in-domain data is more important than the number of training examples and the model architecture. \citet{lai2016generate} found that the corpus domain is more important than the corpus size. Using an in-domain corpus significantly improves the performance for a given task, whereas using a corpus in an unsuitable domain may decrease performance.
Truong et al. encountered a problem in the validation of these in-domain embeddings. The word embedding produced correct document clustering results, leading to the conclusion that these embeddings are of good quality, since they capture the document relatedness needed to create correct clusterings. However unpublished results by Truong et al. state that the embeddings show high error rates on the validation scores. This seems to indicate that the word-vectors are of good quality, but that the available validation metrics fail to confirm this. \citet{Truong2017Thesis} used multiple word similarity validations to asses the quality of the word embeddings. However, these set are created to validate the generic embeddings, they fail to asses the quality of the domain specific embeddings.

\subheader{Research}
To asses the problem of the limited availability of pre-labelled validation sets for domain specific articles, we compare the embeddings to  TF-IDF on a categorization task. This A) gives an indication of the embedding quality for categorization tasks and B) contrasts the performance of embeddings to the performance of the more traditional TF-IDF approach. To ensure the quality of the embeddings for our research, we reuse the embeddings created in the research of \citet{Truong2017Thesis}.
\begin{jumpin}
	\textbf{RQ. 1} Have word-embeddings a higher accuracy for academic texts than TF-IDF for article classification?\\
	\begin{adjustwidth}{0.3in}{}
		\textbf{RQ. 1.1} Does TF-IDF weighting increase the performance of word embedding on academic texts for article classification?\\
		\textbf{RQ. 1.2} Can the usage of alternative distance metrics improve the performance of word embedding on academic articles for article classification?
	\end{adjustwidth}
	\vspace{0.1in}\textbf{RQ. 2} Can word embeddings, combined with pca\footnote{principal component analysis}-based TSNE, create a two-dimensional plot that preserves the journal relatedness?
\end{jumpin}
\subsubheader{Embedding and TF-IDF}
RQ. 1 focusses on the classification results of both embedding-based techniques and TF-IDF.  To measure classification task we use the rank of the class to which the item belongs. Transforming the classification task from a binary metric to a ranking metric. For this task, we will use different versions of embeddings, to answer RQ 1.1, and different TF-IDF versions to not only compare the two techniques, but also look for the optimal results of both techniques. To achieve the optimal results, we compare 20 distance metrics from the SciPy library on ranking performance on the standard embeddings. For this part of the research, we will use the following hypothesis:
\begin{jumpin}
\textit{\textbf{H. 1} Embedding based techniques give lower rankings than the TF-IDF based techniques.}
\begin{jumpin}
\textit{\textbf{H. 1.1} TF-IDF weighted document embeddings outperform standard embeddings on the classification of academic articles.}\\
\textit{\textbf{H. 1.2} Cosine similarity based ranking results in the best performance for the classification of academic articles.}\\
\textit{\textbf{H. 1.3} Word embeddings use less memory while giving better ranking results than TF-IDF on the classification of academic articles.}
\end{jumpin}
\end{jumpin}
By validating our invalidating  these hypotheses we get an indication of the performance of the embeddings compare to older techniques,  get insight into possible performance and resource trade-off's and get insight into the performance of different distance calculation metrics. 
RQ. 2 concerns the visualization of word embeddings and the accuracy of this visualization. To answer this research question, we will use the following hypothesis:
\begin{jumpin}
\textit{\textbf{H. 2} Word embeddings, combined with pca-based TSNE can preserve the journal relatedness on a two dimensional plot.}
\end{jumpin}
The validation of this hypothesis will rely on visual conformation. We expect to see clustering of journals in certain areas, which indicates a research subject. We also expect that articles which are visually close together are closely related by subject. 
\end{document}

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Motivation}
\subheader{In-domain embeddings and validation}
In earlier research concerning domain specific articles,  \citet{Truong2017Thesis} found that in-domain training of the word embeddings can improve the process of document clustering. The usage of in-domain data is more important than the number of training examples and the model architecture. \citet{lai2016generate} found that the corpus domain is more important than the corpus size. Using an in-domain corpus significantly improves the performance for a given task, whereas using a corpus in an unsuitable domain may decrease performance.
Truong et al. encountered a problem in the validation of these in-domain embeddings. The word embedding produced correct document clustering results, leading to the conclusion that these embeddings are of good quality since they capture the document relatedness needed to create correct clusterings. However unpublished results by Truong et al. state that the embeddings show high error rates on the validation scores. This seems to indicate that the word-vectors are of good quality, but that the available validation metrics fail to confirm this. \citet{Truong2017Thesis} used multiple word similarity validations to asses the quality of the word embeddings. However, these sets are created to validate the generic embeddings; they fail to asses the quality of the domain-specific embeddings.

\subheader{Research}
To asses the problem of the limited availability of pre-labeled validation sets for domain-specific articles, we compare the embeddings to  TF-IDF on a categorization task. This A) indicates the embedding quality for categorization tasks and B) contrasts the performance of embeddings to the performance of the more traditional TF-IDF approach. To ensure the quality of the embeddings for our research, we reuse the embeddings created in the research of \citet{Truong2017Thesis}.
\begin{jumpin}
    \textbf{RQ. 1} Have word-embeddings a higher accuracy for academic texts than TF-IDF for article classification?\\
    \begin{adjustwidth}{0.3in}{}
        \textbf{RQ. 1.1} Does TF-IDF weighting increase the performance of word embedding on academic texts for article classification?\\
        \textbf{RQ. 1.2} Can the usage of alternative distance metrics improve the performance of word embedding on academic articles for article classification?
    \end{adjustwidth}
    \vspace{0.1in}\textbf{RQ. 2} Can word embeddings, combined with pca\footnote{principal component analysis}-based TSNE, create a two-dimensional plot that preserves the journal relatedness?
\end{jumpin}
\subsubheader{Embedding and TF-IDF}
RQ. 1 focusses on the classification results of both embedding-based techniques and TF-IDF.  To measure classification task, we use the rank of the class to which the item belongs. This transforms the classification task from a binary metric to a ranking metric. For this task, we will use different versions of embeddings, to answer RQ 1.1, and different TF-IDF versions to not only compare the two techniques but also look for the optimal results of both techniques. To achieve the optimal results, we compare 20 distance metrics from the SciPy library on ranking performance on the standard embeddings. For this part of the research, we will use the following hypothesis:
\begin{jumpin}
\textit{\textbf{H. 1} Embedding based techniques give lower rankings than the TF-IDF based techniques.}
\begin{jumpin}
\textit{\textbf{H. 1.1} TF-IDF weighted document embeddings outperform standard embeddings on the classification of academic articles.}\\
\textit{\textbf{H. 1.2} Cosine similarity based ranking results in the best performance for the classification of academic articles.}\\
\textit{\textbf{H. 1.3} Word embeddings use less memory while giving better ranking results than TF-IDF on the classification of academic articles.}
\end{jumpin}
\end{jumpin}
By validating or invalidating these hypotheses, we get an indication of the performance of the embeddings compared to TF-IDF,  get insight into possible performance and resource trade-off's and get insight into the performance of different distance calculation metrics. 
RQ. 2 concerns the visualization of word embeddings and the accuracy of this visualization. To answer this research question, we will use the following hypothesis:
\begin{jumpin}
\textit{\textbf{H. 2} Word embeddings, combined with PCA-based TSNE can preserve the journal relatedness on a two-dimensional plot.}
\end{jumpin}
The validation of this hypothesis will rely on visual confirmation. We expect to see clustering of journals in certain areas, which indicates a research subject. We also expect that articles which are visually close together are closely related by subject. 
\end{document}
